### 2020-07-23 paper/main.tex
T2 proof

\usepackage{appendix}
\usepackage{todonotes}
\usepackage{wrapfig}
\usepackage{intcalc}

\usepackage{tikz}
\tikzset{%
    simplegraph/.style={every node/.style={draw,circle, inner sep=0pt, minimum size=6mm}},
}
\usetikzlibrary{snakes}
\usetikzlibrary{shapes.geometric}

@@

\newcommand{\TODO}{\todo[inline]}
\newcommand\Lovasz{Lovász }
\newcommand\T{\mathcal{T}}

@@

\paragraph{Configurations of type $\T_2$} A configuration of type $\T_2$ is a six $(v_1, v_2, v_3, v_4, P, X)$, such that:
\begin{itemize}
	\item $v_1v_2v_3v_4$ is a path in $G$.
	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_4\}$-complete nodes.
	\item $P$ is a path in $G\setminus(X \cup \{v_2, v_3\})$ between $v_1$ and $v_4$ and no vertex in $P^*$ is $X$-complete or adjacent to $v_2$ or adjacent to $v_3$.
\end{itemize}

@@

@@

Desctiption.\\

>>>>

\usepackage{appendix}
\usepackage{todonotes}
\usepackage{wrapfig}
\usepackage{intcalc}
\usepackage{amsthm}
\usepackage{cleveref}

\usepackage{tikz}
\tikzset{%
    simplegraph/.style={every node/.style={draw,circle, inner sep=0pt, minimum size=6mm}},
}
\usetikzlibrary{snakes}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{positioning, fit, calc}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

\newcommand{\TODO}{\todo[inline]}
\newcommand\Lovasz{Lovász }
\newcommand\T{\mathcal{T}}
\crefname{lemma}{Lemma}{Lemmas}

@@

\paragraph{Configurations of type $\T_2$}

\begin{wrapfigure}[15]{r}{0.35\textwidth}
	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
		\node(v1) at (0,0) {$v_1$};
		\node(v2) at (1.5,0) {$v_2$};
		\node(v3) at (3,0) {$v_3$};
		\node(v4) at (4.5,0) {$v_4$};

		\draw (v1) to (v2);
		\draw (v2) to (v3);
		\draw (v3) to (v4);

		\tikzset{decoration={snake,amplitude=.6mm,segment length=6mm,
                       post length=0mm,pre length=0mm}}
		\draw[decorate] (v1) to [out=90, in=180] (4.5/2, 3) to [out=0, in=90] (v4);
		\node[draw=none] at (4.5/2, 3.5) {$P$};

		\draw[dashed] (v2) to (.7,2.5);
		\draw[dashed] (v3) to (.7,2.5);
		\draw[dashed] (v2) to (3.8,2.5);
		\draw[dashed] (v3) to (3.8,2.5);

		\node[minimum size=4mm](x1) at (1.2, -2){};
		\node[minimum size=4mm](x2) at (3.3, -2){};
		\node[draw,dotted,inner sep=3pt, circle,yscale=.5, fit={(x1) (x2)},label=below:{$X$}] {};

		\draw[dashed] (x1) to (x2);
		\draw(v1) to (x1);
		\draw(v2) to (x1);
		\draw(v4) to (x1);
		\draw(v1) to (x2);
		\draw(v2) to (x2);
		\draw(v4) to (x2);

		% \draw (a) to (b2);
\end{tikzpicture}
\caption{An example of a $\T_2$.}
\end{wrapfigure}

A configuration of type $\T_2$ is a six $(v_1, v_2, v_3, v_4, P, X)$, such that:
\begin{itemize}
	\item $v_1v_2v_3v_4$ is a path in $G$.
	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_4\}$-complete nodes.
	\item $P$ is a path in $G\setminus(X \cup \{v_2, v_3\})$ between $v_1$ and $v_4$ and no vertex in $P^*$ is $X$-complete or adjacent to $v_2$ or adjacent to $v_3$.
\end{itemize}

@@

To prove that existence of $\T_2$ configuration implies that the graph is not berge, we will need the Roussel-Rubio lemma \cite{RR01} as stated in \cite{MC05} that says:

\begin{lemma}[Roussel-Rubio Lemma]\label{Roussel-Rubio}
	Let $G$ be Berge, $X$ be an anticonnected subset of $V(G)$, $P$ be an odd path $p_1\ldots p_n$ in $G\setminus X$ with length at least 3, such that $p_1$ and $p_n$ are $X$-complete and $p_2, \ldots, p_{n-1}$ are not. Then:
	\begin{itemize}
		\item $P$ is of length at least 5 and there exist nonadjacent $x, y \in X$, such that there are exactly two edges between $x, y$ and $P^*$, namely $xp_2$ and $yp_{n-1}$,
		\item or $P$ is of length 3 and there is an odd antipath joining internal nodes of $P$ with interior in $X$.
	\end{itemize}
\end{lemma}

Now, we shall prove the following:

\begin{lemma}
	If $G$ contains configuration of type $\T_2$ then $G$ is not Berge.
\end{lemma}
\begin{proof}
	Let $(v_1, v_2, v_3, v_4, P, X)$ be a configuration of type $\T_2$. Let us assume that $G$ is not Berge and consider the following:
	\begin{itemize}
		\item If $P$ is even, then $v_1, v_2, v_3, v_4, P, v_1$ is an odd hole,
		\item If $P$ is of length 3. \todo{I merged a couple of proofs from \cite{MC06}, check in the morning if this is correct.} Let us name its nodes $v_1, p_2, p_3, v_4$. It follows from \cref{Roussel-Rubio}, that there exists an odd antipath between $p_2$ and $p_3$ with interior in $X$. We can complete it with $v_2p_2$ and $v_2p_3$ into an odd antihole.
		\item If $P$ is odd with the length of at least 5 \todo{check in the morning}, it follows from \cref{Roussel-Rubio} that we have $x, y \in X$ with only two edges to $P$ being $xp_2$ and $yp_{n-1}$. This gives us an odd hole: $v_2, x, p_2, \ldots, p_{n-1}, y, v_2$.
	\end{itemize} 
\end{proof}

@@

Description.\\
